Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-25 paper/paper.tex
Iterate section 3

TrueTime represents time as a $TTinterval$. A $TTinterval$ is an interval with a
bounded time uncertainty and has two endpoints, i.e., $earliest$ and $latest$,
which are of type $TTstamp$ (which is a timestamp in the context of Spanner).
Table~\ref{tbl:truetime-api} summarizes the three methods provided by the TrueTime
API. However, the most important method is $TT.now()$ which returns a $TTinterval$
which is guaranteed to contain the absolute time of the invocation of $TT.now()$,
i.e., $TT.now().earliest \leq t_{abs}(e) \leq TT.now().latest$, where $e$ denotes
the event of invoking $TT.now()$. More precisely, the absolute time of invocation
of $TT.now()$ is exactly in the middle this $TTinterval$. The interval itself
spans over $2\cdot\epsilon$, where $\epsilon$ denotes the instantaneous error
bound. $\epsilon$ is derived from applied worst-case local clock drift (assumed
to be $200\mu$s/sec). This instantaneous error bound is adjusted over time for
every single machine.

TrueTime uses GPS and atomic clocks as time references. Google chose these two
types of time references because the failure modes of them are uncorrelated. A
datacenter typically consists of multiple \emph{time master} machines. Most of
these are GPS receivers with dedicated antennas. All remaining time master
machines use an atomic clock as reference. Machines using an atomic clock as time
reference are referred to as \emph{Armageddon} masters. The references of all time
masters are compared against each other on a regular basis. To avoid incorrect
time references, time masters also cross-check their local clock drift against
the clock drift of the reference. If these differ too much, the time master evicts
itself.

>>>>

TrueTime represents time as a $TTinterval$. A $TTinterval$ is an interval with a
bounded time uncertainty and has two endpoints, $earliest$ and $latest$, which
are of type $TTstamp$ (a timestamp in the context of Spanner).
Table~\ref{tbl:truetime-api} summarizes the three methods provided by the TrueTime
API. However, the most important method is $TT.now()$. i$TT.now()$ which returns
a $TTinterval$ which is guaranteed to contain the absolute time of the invocation
of $TT.now()$, i.e., $TT.now().earliest \leq t_{abs}(e) \leq TT.now().latest$,
where $e$ denotes the event of invoking $TT.now()$. More precisely, the absolute
time of invocation of $TT.now()$ is exactly in the middle this $TTinterval$. The
interval itself spans over $2\cdot\epsilon$, where $\epsilon$ denotes the
instantaneous error bound. $\epsilon$ is derived from applied worst-case local
clock drift (assumed to be $200\mu$s/sec). This instantaneous error bound is
adjusted over time for every single machine.

TrueTime uses GPS and atomic clocks as time references. Google chose these two
types of time references because the failure modes of them are uncorrelated. A
datacenter typically maintains multiple \emph{time master} machines. Most of
these are GPS receivers with dedicated antennas. All remaining time master
machines use an atomic clock as reference. Machines using an atomic clock as time
reference are referred to as \emph{Armageddon} masters. The references of all time
masters are compared against each other on a regular basis. To avoid incorrect
time references, time masters also cross-check their local clock drift against
the clock drift of the reference. If these differ too much, the time master evicts
itself.
